---
title: "Analysis"
author: "Tom Yedwab"
date: "August 18, 2016"
output: pdf_document
---

# Read in data

```{r}
library(ggplot2)
processed <- read.csv("~/source/berkeleymidsreview/export_data/processed.csv")
```

# Data cleanup

```{r}
# Parse some binaries so R recognizes them as such
processed$MobileBin = processed$Mobile. == "True"
processed$ScrolledBin = processed$Scrolled. == "True"
processed$DismissedBin = processed$Dismissed. == "True"
processed$DisclosureBin = processed$Show.Disclosure == "True"
processed$DialogBin = processed$Show.Dialog == "True"

# Pages viewed have to be at least 1, otherwise we wouldn't be recording data for the subject
processed[processed$Pages.Viewed == 0, "Pages.Viewed"] = 1

# Define a "bounce" as only viewing one page, no scrolling
processed$Bounce = processed$Pages.Viewed < 2 & !processed$ScrolledBin
```

# Randomization check: These should be close to 0.5

```{r}
mean(processed$DisclosureBin)
mean(processed$DialogBin)
```

# Look at the distributions of outcome variables in treatment/control

Total Page Time:
```{r}
processedSubset = processed[processed$Total.Page.Time <= 600,]
ggplot(processedSubset, aes(Total.Page.Time)) + geom_histogram() + facet_grid(DisclosureBin ~ .)
ggplot(processedSubset, aes(log(Total.Page.Time))) + geom_histogram() + facet_grid(DisclosureBin ~ .)
qqnorm(processedSubset$Total.Page.Time)
```

Pages Viewed:
```{r}
ggplot(processed, aes(Pages.Viewed)) + geom_histogram(binwidth=1) + facet_grid(DisclosureBin ~ .)
ggplot(processed, aes(log(Pages.Viewed))) + geom_histogram(binwidth=1) + facet_grid(DisclosureBin ~ .)
qqnorm(processedSubset$Pages.Viewed)
```

# Estimate some effects
```{r}
time.m = lm(Total.Page.Time ~ DisclosureBin + DialogBin + 
              DisclosureBin * DialogBin + Source + MobileBin +
              Age + Gender, data=processed)
pages.m = lm(log(Pages.Viewed) ~ DisclosureBin + DialogBin + 
               DisclosureBin * DialogBin + Source + MobileBin +
               Age + Gender, data=processed)
scrolled.m = glm(ScrolledBin ~ DisclosureBin + DialogBin +
                   DisclosureBin * DialogBin + Source + MobileBin +
                   Age + Gender, data=processed, family=binomial(link='logit'))
dismissed.m =  glm(DismissedBin ~ DisclosureBin + DialogBin +
                     DisclosureBin * DialogBin + Source + MobileBin +
                     Age + Gender, data=processed, family=binomial(link='logit'))
bounce.m =  glm(Bounce ~ DisclosureBin + DialogBin +
                     DisclosureBin * DialogBin + Source + MobileBin +
                     Age + Gender, data=processed, family=binomial(link='logit'))
```

```{r}
summary(time.m)
summary(pages.m)
summary(scrolled.m)
summary(dismissed.m)
summary(bounce.m)
```

# Statistical power checks

```{r}
simulate.regression <- function(mean.control, sd, treatment.effect, n) {
  tbl = data.frame(
    group=c(rep(0, n/2), rep(1, n/2)),
    val=c(rnorm(n/2, mean=mean.control, sd=sd),
          rnorm(n/2, mean=mean.control+treatment.effect, sd=sd)))
  model = lm(val ~ group, data=tbl)
  p.value = summary(model)$coefficients[2,4]
  return(p.value)
}

calculate.power <- function(mean.control, sd, treatment.effect, n) {
  p.value.distribution = replicate(
    10000,
    simulate.regression(mean.control, sd, treatment.effect, n))
  return(mean(p.value.distribution < 0.05))
}
```

# What is our statistical power to detect a 10% increase/decrease in total page time?

```{r}
cov.model = lm(Total.Page.Time ~ Source + MobileBin + Age + Gender, data=processed)
processed$Total.Page.Time.Prediction = predict(cov.model, processed)
processed$Total.Page.Time.Resid = processed$Total.Page.Time.Prediction - processed$Total.Page.Time

mean.value = mean(processed[processed$DisclosureBin==F,"Total.Page.Time"])
mean.control = mean(processed[processed$DisclosureBin==F,"Total.Page.Time.Resid"])
sd.control = sd(processed[processed$DisclosureBin==F,"Total.Page.Time.Resid"])
treatment.effect = mean.value * -0.1
time.power = calculate.power(mean.control, sd.control, treatment.effect,
                             nrow(processed))
print(time.power)
```

# What is our statistical power to detect a 10% increase/decrease in pages viewed?

```{r}
cov.model = lm(log(Pages.Viewed) ~ Source + MobileBin + Age + Gender, data=processed)
processed$Pages.Viewed.Prediction = predict(cov.model, processed)
processed$Pages.Viewed.Resid = processed$Pages.Viewed.Prediction - processed$Pages.Viewed

mean.value = mean(log(processed[processed$DisclosureBin==F,"Pages.Viewed"]))
mean.control = mean(processed[processed$DisclosureBin==F,"Pages.Viewed.Resid"])
sd.control = sd(processed[processed$DisclosureBin==F,"Pages.Viewed.Resid"])
# Increase of log(1.1) = 0.04
treatment.effect = mean.value * 0.04
pages.power = calculate.power(mean.control, sd.control, treatment.effect,
                              nrow(processed))
print(pages.power)
```

# What is our statistical power to detect a 10% increase/decrease in bounce rate?

```{r}
simulate.logistic.regression <- function(control.p, treatment.p, n) {
  tbl = data.frame(
    group=c(rep(0, n/2), rep(1, n/2)),
    val=c(runif(n/2, 0, 1) <= control.p,
          runif(n/2, 0, 1) <= treatment.p))
  model = glm(val ~ group, data=tbl, family=binomial(link='logit'))
  p.value = summary(model)$coefficients[2,4]
  est = summary(model)$coefficients[2,1]
  return(p.value)
}

calculate.logistic.power <- function(control.p, treatment.p, n) {
  p.value.distribution = replicate(
    10000,
    simulate.logistic.regression(control.p, treatment.p, n))
  return(mean(p.value.distribution < 0.05))
}

control.p = mean(processed[processed$DisclosureBin==F,"Bounce"])
treatment.p = control.p * 1.10
bounce.power = calculate.logistic.power(control.p, treatment.p, nrow(processed))
print(bounce.power)
```


